An Authoritative Adventure

### 2022-08-31 article.tex
Added note on single column DndMonster.
Bit of layout for the monster tables; still bad, needs work

\section{Monsters and NPCs}

% Monster stat block
\begin{DndMonster}[float=t]{Monster Foo}
  \DndMonsterType{Medium aberration (metasyntactic variable), neutral evil}

@@

The |DndMonster| environment is used to typeset monster and NPC stat blocks. The module supplies many functions to easily typeset the contents of the stat block

>>>>

\clearpage

\section{Monsters and NPCs}
The |DndMonster| environment is used to typeset monster and NPC stat blocks. The module supplies many functions to easily typeset the contents of the stat block.

The stat block can be formatted either as a single column, or as a block that spans the page horizontally.

% Monster stat block
\begin{DndMonster}[float=h]{Monster Foo}
  \DndMonsterType{Medium aberration (metasyntactic variable), neutral evil}

@@

\clearpage
